---
title: "Data Analysis 01 Template"
author: "Ashkan Motamedi"
date: "3/8/2021"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 

In this notebook, we are reverse engineering the story, FAs police struggle to solve homicides, Baltimore residents see an ‘open season for killing’, from the Washington Post [As police struggle to solve homicides, Baltimore residents see an ‘open season for killing](https://www.washingtonpost.com/investigations/as-police-struggle-to-solve-homicides-baltimore-residents-see-an-open-season-for-killing/2018/12/26/7ee561e4-fb24-11e8-8c9a-860ce2a8148f_story.html)
## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
```

## Load and Cleaning Data

[In this block of text, describe the source of the data, and write a basic data dictionary for data you are working with]

```{r}
# Load required data
# Path to data should be loaded from folder "data" i.e. 
homicide_data <- read.csv("data/homicide-data.csv")

# Clean required data and prepare for analysis if needed. 


```

## Sentences to Engineer
In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 2

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 3

* **Sentence text**: [Baltimore is also one of 30 cities that have seen an increase in homicides in recent years, with the greatest raw number increase in killings of any city other than Chicago, which has four times the population. While homicide rates remain near historical lows in most American cities, Baltimore and Chicago are now both seeing murder tallies that rival the early 2000s.]
* **Analysis summary**: In running the data I found that 2014 was the year Baltimore lead Chicago 236 to 129. However, I was unable to confirm the findings of this data as only 25 states saw an increase in homicides in 2014. No year ran meant the required 30 as mentioned in the story 2014 was the closest with 25 when subtracted by 2017 

```{r}
# Put code to reverse engineer sentence here

total_homicide_2014 <- homicide_data %>%
  select(reported_date, city, state, disposition) %>%
  filter(reported_date %in% 20140101:20141231) %>%
  group_by(city) %>%
  summarise(total_cases_2014=n())
total_homicide_2017 <- homicide_data %>%
  select(reported_date, city, state, disposition) %>%
  filter(reported_date %in% 20170101:20171231) %>%
  group_by(city) %>%
  summarise(total_cases_2017=n())
total_homicide_arrest_<- total_homicide_2014 %>%
  inner_join(total_homicide_2017) %>%
  mutate(increase_in_homicides_2014  =  total_cases_2017 - total_cases_2014) %>%
  select(city,increase_in_homicides_2014) %>%
  arrange(desc(increase_in_homicides_2014))


  
 
  

# Display results of code below this codeblock

```

### Sentence 4

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

* **Sentence text**: [Paste in sentence to engineer here]
* **Analysis summary**: [Write up two to three sentences describing the results of your analysis.  Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-